Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
Update Final-Draft.Rmd

model_2 <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (1 | State), 
  data = model_data, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

@@

@@

@@

@@

@@

>>>>

model_3 <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (1 | State), 
  data = model_data, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

##mcmc_ stable
```{r}
mcmc_trace(RM_model)
mcmc_dens_overlay(RM_model) 
```

@@

```{r}
pp_check(RM_model)
```

@@

```{r}
mcmc_trace(NR_model)
mcmc_dens_overlay(NR_model) 
```
##ppcheck

@@

```{r}
mcmc_trace(model_3)
mcmc_dens_overlay(model_3) 
```

##ppcheck
```{r}
pp_check(model_3)
```

@@

```{r}
mcmc_trace(complexmod)
mcmc_dens_overlay(complexmod) 
```

@@

```{r}
pp_check(complexmod)
```
